Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-03-26 paper/verification-conditions.tex

If all the verification conditions hold (AGREE uses $k$-inductive
model checking to automatically prove or disprove each generated
verification condition), then the system is said to be \emph{correct},
meaning that the system composition meets input assumptions at each
input as well as the guarantees on the system output. A consequence of
this result is that $\globally(\historically(\assumes) \implies
\guarantees)$ holds for the system contract.
Therefore the Liskhov substitution principle applies, and as such, the implementation is a safe substitution for the system contract \cite{10.1145/62139.62141}.

>>>>

If all the verification conditions hold (AGREE uses $k$-inductive
model checking to automatically prove or disprove each generated
verification condition), then the system is said to be \emph{correct},
meaning that the system composition meets input assumptions at each
input as well as the guarantees on the system output. A consequence of
this result is that $\globally(\historically(\assumes) \implies
\guarantees)$ holds for the system contract.
Therefore the Liskov substitution principle applies, and as such, the implementation is a safe substitution for the system contract \cite{10.1145/62139.62141}.
